Certified Symbolic Finite Transducers: Formalization and Applications to String Analysis

### 2025-09-10 Paper/introduction.tex
Something wrong with the example

To evaluate the effectiveness and efficiency of our formalization, we 
provide two applications: (1) analysis of the sanitizer \texttt{HTMLdecode},
which is used for preventing XSS attacks, and (2) an SMT-LIB \cite{smtlib}
compliant certified string solver handling equality, concatenation, regular
constraints, and more important the string replaceall operator, which has been
argued to be indispensable for analysis of XSS 
\cite{DBLP:conf/popl/LinB16,Kern,Berkeley-JavaScript,DBLP:conf/sp/SaxenaAHMMS10,uss/HooimeijerLMSV11}).
The experimental results demonstrate that our formalization achieves computational efficiency in constraint-solving scenarios.

>>>>

To evaluate the effectiveness and efficiency of our formalization, we 
provide two applications: (1) analysis of the sanitizer \texttt{HTMLdecode},
which is used for preventing XSS attacks, and (2) an SMT-LIB \cite{smtlib}
compliant certified string solver handling equality, concatenation, regular
constraints, and more importantly the string replaceall operator, which has been
argued to be indispensable for analysis of XSS 
\cite{DBLP:conf/popl/LinB16,Kern,Berkeley-JavaScript,DBLP:conf/sp/SaxenaAHMMS10,uss/HooimeijerLMSV11}).
The experimental results demonstrate that our formalization achieves computational efficiency in constraint-solving scenarios.
